Planar Maximal Covering with Ellipses

### 2019-04-25 quali/quali.presentation/slides.tex
WIP

%\usepackage{hyperref}
%\usepackage{tikz}

@@

\begin{frame}
\frametitle{Sumário}
 \tableofcontents
\end{frame}

\section{Introdução}
\begin{frame}
\frametitle{Introdução}
\begin{itemize}
	\item Problemas de cobertura
	\begin{itemize}
		%\item Cobertura mínima
		\item Cobertura maximal
	\end{itemize}
	\item Maximal Covering Location Problem (MCLP)
	\item Planar Maximal Covering Location Problem (PMCLP)
	\begin{itemize}
	\item Um disco: algoritmos $\bigO(n^2)$ e $\bigO(n^2\log{n})$
	\item $m$ discos: algoritmo $\bigO(n^{2m-1}\log{n})$
	\end{itemize}
	\item Objetivos
	\begin{itemize}
		\item Desenvolver algoritmo $\bigO(n^2\log{n})$ para um disco
		\item Adaptar o algoritmo para o caso com $m$ ellipses
	\end{itemize}
\end{itemize}

@@

\section{Preliminares}

\begin{frame}
	\frametitle{Preliminares}
	\begin{block}{Norma Euclidiana}
		Seja $u \in \R^2$

		\begin{equation*}
		||u||_2 = \sqrt{u^Tu}
		\end{equation*}

	\end{block}

\begin{block}{Norma Elíptica}
	Seja $u \in \R^2$ e $Q$ uma matriz $2x2$ positiva definida

	\begin{equation*}
	||u||_{Q} = \sqrt{u^TQu}
	\end{equation*}
\end{block}
\end{frame}

\begin{frame}{Preliminares}
	\begin{block}{Disco}
		content...
	\end{block}

	\begin{block}{Ellipse}
		content...
	\end{block}
\end{frame}

\section{Cobertura Maximal por Discos}
\begin{frame}{Cobertura maximal por discos}{Um disco}
	content... trabalhos passados e motivacao
\end{frame}

\section{Cobertura Maximal por Discos}
\begin{frame}{Cobertura maximal por discos}{Um disco}
	content... meu algoritmo
\end{frame}

>>>>

%\usepackage{hyperref}
\usepackage{tikz}
\usetikzlibrary{quotes, angles, intersections}

@@

\begin{frame}
\frametitle{Contents}
 \tableofcontents
\end{frame}

\section{Introdução}
\begin{frame}
\frametitle{Introdução}
\begin{itemize}
	\item Covering problems
	\begin{itemize}
		\item Set Cover Problem
		\item Maximal Covering Problem
	\end{itemize}
	\item Maximal Covering Location Problem (MCLP)
	\item Planar Maximal Covering Location Problem (PMCLP)
	\begin{itemize}
	\item One disk: $\bigO(n^2)$ and $\bigO(n^2\log{n})$ algorithms
	\item $m$ disks: $\bigO(n^{2m-1}\log{n})$ algorithm
	\end{itemize}
	\item Goals
	\begin{itemize}
		\item Develop a $\bigO(n^2\log{n})$ algorithm for the one disk case
		\item Adapt it for the $m$ ellipses case
	\end{itemize}
\end{itemize}

@@

\section{Preliminaries}

\begin{frame}{Preliminaries}

	\begin{block}{Norms}
		Let $u \in \R^2$ and $Q$ a $2$ by $2$ positive definite matrix
		\begin{itemize}
			\item Euclidean
			\begin{equation*}
			||u||_2 = \sqrt{u^Tu}
			\end{equation*}

			\item Elliptical
			\begin{equation*}
			||u||_{Q} = \sqrt{u^TQu}
			\end{equation*}
		\end{itemize}
	\end{block}

\begin{frame}{Preliminaries}

	\begin{block}{Ellipse}
		Given a center $c \in \R^2$ and a p.d. matrix $Q$, an ellipse is the set of points that satisfy

		\begin{equation*}
		||u-c||_Q = 1
		\end{equation*}

		with $\le$ representing the set of covered points
	\end{block}

	\begin{block}{Axis-parallel ellipse}
		Any $2$ by $2$ diagonal d.p. matrix determines an axis-parallel ellipse, which can also be described by

		\begin{equation*}
		\frac{(x-c_x)^2}{a^2} + \frac{(y-c_y)^2}{b^2} = 1
		\end{equation*}
	\end{block}

\begin{frame}{Preliminaries}
	\begin{figure}[H]
		\centering

		\caption{Three curves representing the points that have distance equal to one.}
		\input{figures/a.tex}
		%\fautor
		\label{fig:3ellipses_intersect}
	\end{figure}
\end{frame}

\section{Maximal Covering by Disks}
\begin{frame}{Maximal Covering by Disks}{One disk}

	$MCD(\Pp, 1)$ is the problem of placing one disk on the plane to cover a subset of a demand set $\Pp$ maximizing the weights of the covered points.

	\begin{equation*}\label{eq:max_one_disk}
		\max_q w(\Pp \cap D(q)),
	\end{equation*}

	\begin{itemize}
		\item $\Pp=\{p_1,\dots,p_n\}$ is the demand set with weights $w(p_i)>0$
		\item $w(A)$, with $A\subset \Pp$ is the sum of weights of the points in $A$
		\item $D(q)$ is a disk with radius one with center at point $q$
		\item We will introduce an equivalent problem...
	\end{itemize}
\end{frame}

\subsection{Maximum Weight Clique Problem}
\begin{frame}{Maximum Weight Clique Problem}
	Let $\D=\{D_1,\dots,D_n\}$ be a set of $n$ unit disks with weights $w_i>0$. The maximum weight clique is defined as

	\begin{equation*}
	\max_q \sum_{D_k \cap q \neq \emptyset} w_k,
	\end{equation*}

	\begin{itemize}
		\item The disks are fixed at $\Pp =\{p_1,\dots,p_n\}$ with $w_k=w(p_k)$
		\item A clique is a non-empty intersection area of a subset of disks
		\item An optimal solution for the maximum weight clique is an optimal solution for $MCD(\Pp,1)$.
	\end{itemize}
\end{frame}
